---
title: "Analysis of 4 central criteria of PCRs"
author: "César Montiel Olea"
date: "Ocotber 15, 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# We analyze the 4 central criteria

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 0. Install packages

```{r,message=FALSE,warning=FALSE}
if (!require("tidytext")) install.packages("tidytext"); library("tidytext")
if (!require("tidymodels")) install.packages("tidymodels"); library("tidymodels")
if (!require("tidyverse")) install.packages("tidyverse"); library("tidyverse")
if (!require("reshape2")) install.packages("reshape2"); library("reshape2")
if (!require("ggrepel")) install.packages("ggrepel"); library("ggrepel")
if (!require("topicmodels")) install.packages("topicmodels"); library("topicmodels")
if (!require("SnowballC")) install.packages("SnowballC"); library("SnowballC")
if (!require("magrittr")) install.packages("magrittr"); library("magrittr")
if (!require("stopwords")) install.packages("stopwords"); library("stopwords")
if (!require("widyr")) install.packages("widyr"); library("widyr")
if (!require("tidygraph")) install.packages("tidygraph"); library("tidygraph")
if (!require("lubridate")) install.packages("lubridate"); library("lubridate")
if (!require("pdftools")) install.packages("pdftools"); library("pdftools")
#if (!require("openNLP")) install.packages("openNLP"); library("openNLP")
if (!require("cleanNLP")) install.packages("cleanNLP"); library("cleanNLP")
if (!require("readxl")) install.packages("readxl"); library("readxl")
if (!require("dplyr")) install.packages("dplyr"); library("dplyr")
if (!require("doParallel")) install.packages("doParallel"); library("doParallel")
if (!require("foreach")) install.packages("foreach"); library("foreach")
if (!require("iterators")) install.packages("iterators"); library("iterators")
if (!require("parallel")) install.packages("parallel"); library("parallel")
if (!require("tm")) install.packages("tm"); library("tm")
if (!require("tabulizer")) install.packages("tabulizer"); library("tabulizer")
if (!require("stringi")) install.packages("stringi"); library("stringi")
if (!require("purrr")) install.packages("purrr"); library("purrr")
if (!require("quanteda")) install.packages("quanteda"); library("quanteda")
if (!require("tibble")) install.packages("tibble"); library("tibble")
if (!require("stringi")) install.packages("stringi"); library("stringi")
if (!require("stringr")) install.packages("stringr"); library("stringr")
if (!require("wordcloud")) install.packages("wordcloud"); library("wordcloud")
if (!require("ggplot2")) install.packages("ggplot2"); library("ggplot2")
if (!require("tidyr")) install.packages("tidyr"); library("tidyr")
if (!require("janeaustenr")) install.packages("janeaustenr"); library("janeaustenr")
if (!require("igraph")) install.packages("igraph"); library("igraph")
if (!require("tokenizers")) install.packages("tokenizers"); library("tokenizers")
if (!require("tidylo")) install.packages("tidylo"); library("tidylo")
if (!require("rstatix")) install.packages("rstatix"); library("rstatix")
if (!require("brio")) install.packages("brio"); library("brio")

devtools::install_github("thomasp85/ggraph")
pkgbuild::check_build_tools(debug = TRUE)
if (!require("ggraph")) install.packages("ggraph"); library("ggraph")

install.packages("remotes")
remotes::install_github("dgrtwo/drlib")
if (!require("drlib")) install.packages("drlib"); library("drlib")


```


## 1. Preprocess the data

# Loading the text files

```{r}
path <-"C:/Users/CESARMO/OneDrive - Inter-American Development Bank Group/Desktop/NLP_IDB/NLP_IDB"
setwd(path)
library(doParallel)
library(foreach)
library(iterators)
library(parallel)

# We read the text files
files <- dir(paste0(path, "/all_data/"), 
             pattern = "\\.txt", full.names = TRUE)
outlist <- rep(list(list()), length(files)) # we create an outlist to store the files

for (i in 1:length(files))  {
  outlist[[i]] <- base::readLines(files[i], encoding = 'latin1')  %>%
  str_replace("[:space:][:blank:]", "") %>%
    removeNumbers() %>%
    str_replace_all("-", " ") %>%
    str_replace_all("-", " ") %>%
    #str_replace_all("???", " ") %>%
    str_replace_all('"', " ") %>%
    str_replace_all("á", "a") %>%
    str_replace_all("é", "e") %>%
    str_replace_all("í", "i") %>%
    str_replace_all("ó", "o") %>%
    str_replace_all("ú", "u") %>%
    str_replace_all("Á", "A") %>%
    str_replace_all("É", "E") %>%
    str_replace_all("Í", "I") %>%
    str_replace_all("Ó", "O") %>%
    str_replace_all("Ú", "U")  %>%
    str_replace_all("º", "") %>%
    str_replace_all("°", "") %>%
    str_replace_all("¨", "") %>%
    str_replace_all("¿", "") %>%
    #str_replace_all(".", "") %>%
    #str_replace_all("""", "") %>%
    removePunctuation() %>%
    stripWhitespace()
  }
 
# stopCluster(cl)

```

# Cleaning and Using regular expressions to trim the text

```{r}
library(purrr)
library(stringi)
library(stringr)
outlist <- map(outlist, paste, collapse = " ") # we paste each sentence into a single vector

# We remove special characters 
outlist <- map(outlist, ~ stringr::str_replace(.x, "[:space:][:blank:]", ""))
outlist <- map(outlist, ~ stringr::str_replace_all(.x, "\'", ""))
outlist <- map(outlist, ~ stringr::str_replace_all(.x, '\"', ""))
outlist <- map(outlist, ~ stringr::str_replace_all(.x, "http\\S+\\s*","")) # remove hyperlinks
outlist <- map(outlist, ~ stringr::str_replace_all(.x, "[^a-zA-Z0-9\\s]+","")) 
outlist <- map(outlist, ~ stringr::str_replace(.x, "\\b[[:alpha:]]{1,3}\\b", "")) 

#outlist <- map(outlist, ~ stringr::str_replace_all(.x, "[IVXLCM]+","")) 

new_outlist <- rep(list(list()), length(outlist)) # we create another list to store the files
#prueba <- c("https://direccion http://otradireccion informe' informe relevancia abc")

#NOTA: DR-L1057 se le agregó la palabra Criterios Centrales

for (i in 1:length(outlist))  { 
  new_outlist[[i]] <- str_replace(outlist[[i]], ".*?CRITERIOS|.*?Criterios", "")
  new_outlist[[i]] <- str_replace(new_outlist[[i]], ".*?Relevancia", "")
  new_outlist[[i]] <- str_replace(new_outlist[[i]], "CRITERIOS.*\\w+|Criterios.*\\w+", "")
}


# we can also use the map function
#new_outlist <- map(outlist, ~ stringr::str_replace(.x, ".*?CRITERIOS|.*?Criterios", "")) 
#new_outlist <- map(new_outlist, ~ stringr::str_replace(.x, ".*?Relevancia", "")) 
#new_outlist <- map(new_outlist, ~stringr::str_replace(.x, "CRITERIOS.*\\w+|Criterios.*\\w+", "")) 
                                          
more_stopping <- c('año','usd','i','ii','iii','co','fin','mill','vez','si','l','tener','oc','iv','nuevos','problema','santa','dio','p','enero','febrero','marzo','abril','mayo','juni','juli','agosto','septiembr','octubr','noviembr','diciembr','ende','tipo','fase','costo','existe','lográ','v','acerca','b','entrada','forma','gran','igualmente','misma','orden','oficina','output','podr','reporte','san','tercer','térmico','zonas','caja','alrededor','asignados','decir','después','dicha','lleva','maestro','solo','supuesto','with','working','alto','asociado','dichos','escasa','fa','figura','genera','km','llevado','medidas','menos','modo','municipio','necesarias','partir','pese','personas','pmasis','presentar','previas','previstos','real','realizando','sentido','suscrito','tema','acorde','acorde','actividad','atención','cuarto','efectos','entonces','especial','crítica','existen','incluido','lograr','logro','luego','mayores','mecanismo','mejor','notable','nuevas','objeto','oferta','original','pari','passu','red','conjunto','crea','cuatro','darle','estima','gestor','igual','indica','informa','interno','internos','largo','llega','lugar','manual','mismas','mll','obtener','plazos','presenta','puedan','realizada', "semanas",'tales','todas','todo','tomo','abstuvo','afecta','apenas','apoya','c','buena','centros','compromisos','conjunta','considerablemente','consorcio','contenido','continua','cronograma','deben','deberán','dialogo','disponibles','dificultad','documentos','ejercicio','elegible','ello','esfuerzos','espacios','especiales','esquemas','etapas','formalizá','financiada','fuertes','funcionamiento','generado','generados','generar','generá','gerencial','gestiones','gestores','grupos','haber','hecho','inicios','manifestado','mencionados','opinión','partes','pendiente','permitieran','podra','presentan','presentando','proyectados','punto','puesta','reporta','respuesta','revisaron','sigue','sigue','solo','superior','sustancial','torno','tramitar','tres','utilización','ve','vi','vio','acordado','actualizado','adecuado','agencia','ahora','ajustar','alcanzado','alcanzarán','ambos','anteriores','aplicativo','aportes','apoyar','aprobar','asimismo','atender','calculado','cercano','cinco','continuar','corresponden','cumplido','da','dará','deberá','decida','decididas','definido','definidas','denominada','determinar','detalles','detalle','diferencias','dinamismo','directivas',"disponibilidad")

more_stopping2 <- c("a", "x", "rp", "p", "rnº", "nº", "na", "i", "rn", " ", 
                "ser", "mas", "asi", "hallazgo","aaps", "aboal", "and", "report",
                "sistemas", "debe", "así", "cada", "bien", "polit", "termin",
                "of","the", "uso", "manera", "caso", "puede", "inta", "paps", "if",
                "js", "ae", "fiit", "ee", "ors", "aps", "categoria", "parte",
                "recomienda", "shf", "nº", "pam", "sence", "ap", "producto", "r",
                "dos", "contar", "debiese", "muchas", "características", "mediante",
                "base","na", "importante", "pa", "us", "tabla", "meta", "metas",
                "años", "bid", "resultado", "unidad", "través", "bajo", "pcr",
                "ptmc", "mides", "rdo", "o", "cs", "fie", "según", "º",
                "banco", "total","mides", "simtramss", "sence", "smsxxi", "bandesal",
                "satisf", "fira", "ceibal", "mgap", "gualac", "bonit", "etcs",
                "bancoldex", "profip", "mtop", "buscador", "enee", "mcsa",
                "fpgc", "sitramss", "inifap", "prosoli", "snip", "mifan",
                "probid", "mrecic", "sinat", "sidif", "remediar", "pace",
                "psci", "empopast", "senc", "ferum", "nios", "cort", "ministeri",
                "salvador", "otorg", "encuest", "tram", "manej", "siaf", "piris",
                "event", "comun", "colombi", "educ", "hondur", "logist", "minfin",
                "esteb", "tram", "montevide", "club", "visit", "beneficiari",
                "silais", "puent", "enel" , "vial", "nios", "joven", "senasb",
                "past", "millon", "atraccion", "remedi", "elimin", "niez", "direccion",
                "expres", "post", "elimin", "mism", "trav", "plaz", "tabl", "neral", 
                "medi", "equip", "pued", "nivel", "valor", "final", "logr", "sector",
                "tambi", "atencion", "alcanz", "asoci", "mayor", "menor", "idem",
                "respect", "gener", "numer", "accion", "nuev", "esper", "nicaragu",
                "unid", "utiliz", "millon", "consider", "inici", "segun", "direct",
                "neces", "period", "merc", "banc", "permit", "activ", "import", "inec",
                "observ", "segund", "cuent", "primer", "form", "observ", "personal",
                "previst", "present", "prosap", "epsa", "chil", "anni", "formos", "mendoz",
                 "emit", "mins", "dsip", "ecuador", "anii", "pder", "mspas", "caipi", "certez",
                "apan", "dpvs", "sesal", "ansv", "screi", "piri", "plsv", "copec", "ecnt", 
                "conami", "filtracion", "inform", "sagarp", "caps", "pdfor", "coloni",
                "tras", "risk", "colombian", "udududud", "bogot", "kluv", "mhcp", "usmm",
                "argentin", "cion", "index", "gwha", "juan", "panam", "checklist","world",
                "nent", "rrhh", "dominican", "marn", "siol", "guayaquil", "udududud",
                "gwha", "health", "anrs", "amss", "ipsa", "guatemal", "senplad", "measur",
                "city", "tenis", "pntc", "energy", "paap", "conelec", "sigs", "tegucigalp",
                "mmay", "uruguay", "mtps", "igrm", "usveh", "paraguay", "olanch", "ebitd",
                "cntt", "paysri", "minsal", "segovi", "bolivi", "mosc", "siub", "park",
                "siboif", "nias", "pech", "epsas", "soyapang", "rcvg", "chilen", "paml",
                "sucre", "cochabamb", "meer", "ensmi", "haiti", "ecmac", "apps", "dgsg",
                "stps", "proc", "mteps", "mteps", "trujill", "vmee", "pevd", "mrec", 
                "daafim", "conap", "dissur", "disnort", "onsv", "rios", "iger", "mexic", "revis",
                "gadm", "secop", "anep", "snap", "ucar", "sigap", "babahoy", "snbs",
                "panam", "misicuni", "prsv", "anda", "senas", "prossapys", "padill",
                "bols", "espej", "lotif", "enatrel", "neuchatel", "leas", "ugand", "dgsa",
                "hotel", "inclu", "porcentaj", "asim", "ingles", "mont", "cierr", "recib",
                "ultim", "moment", "clasific", "calific", "unic", "inse", "residual", "cond",
                "fuari", "electron", "actual", "rieg","residual", "cond", "frent",
                 "porcent", "punt", "sectorial", "necesari", "seal", "dire", "diferent",
                 "semestral", "ampli", "compr", "encuentr", "estrateg", "analisis",
                "tratamient", "estim", "incorpor", "atend", "elabor", "intermedi", "enriqu",
                "encontr", "busc", "lempir", "catastr", "aguil", "cerrat", "intibuc",
                "prestam", "ejecut", "desempe", "dias", "pagin", "avanc", "coordin")


mystopwords <- c(more_stopping, more_stopping2)
```


# Converting lists of words into dataframes

```{r}
library(tm)
library(quanteda)
new_files <- dir(paste0(path, "/all_data"), pattern = "\\.txt")

df <- rep(list(data.frame()), length(outlist)) # we create an empty dataframe

for (i in 1:length(new_outlist))  {
  df[[i]] <- as.data.frame(unlist(new_outlist[i]))
  df[[i]]$name <- as.factor(substr(new_files[[i]], 1, 8))
  colnames(df[[i]]) <- c("word", "name")
  df[[i]]$word <- as.character(df[[i]]$word)
}
 
full_text <- tibble()
 
for (i in 1:length(df)) {
  full_text <- bind_rows(full_text, df[[i]])
}
 
# df.corpus <- full_text %>%
#   rename(text = word) %>%
#   corpus()
#  
#summary(df.corpus) # summarizing corpus
 
```

## 2. Analysis of raw data

# 2.1 Total words in PCR per year (no preprocess applied)

# Loading OVE data

```{r}
library(foreign)
data <- read.csv(paste0(path, "/data/data_clean.csv"))

data <- data%>%
  mutate_if(is.character, as.factor)
  
#data$relevance_rate <- as.factor(data$OVERelevancerating)
#data$ove_rating <- as.factor(data$OVERating)
data$CO_year <- as.factor(data$CO_year)
data$name <- as.character(data$OperNumber) 

# We create dummies for Successful and Unsuccessful PCRs according to MGT and OVE
data$dummy_exitoso_OVE <- ifelse(data$OVERating == "Highly Successful" |
                                  data$OVERating == "Successful" |
                                  data$OVERating == "Partly Successful", 1, 0)


data$dummy_exitoso_OVE <- factor(data$dummy_exitoso_OVE, 
                                 labels = c("Unsuccessful", "Successful"))

data$dummy_exitoso_MGT <- ifelse(data$IDBManagementRating == "Highly successful" |
                                  data$IDBManagementRating == "Successful" |
                                  data$IDBManagementRating == "Partly successful" | 
                                  data$IDBManagementRating == "Partly Successful", 1, 0)

data$dummy_exitoso_MGT <- factor(data$dummy_exitoso_MGT, 
                                 labels = c("Unsuccessful", "Successful"))



```

# creating figures and tables

```{r}
library(tidyverse)
library(rstatix)
tot_words <- full_text %>%
  unnest_tokens(word, word)%>%
  add_count(name, name = "total_words") %>%
  group_by(name, total_words) %>%
  count(word, sort = TRUE) %>%
  ungroup()

tot_words[order(tot_words$total_words), ] 
tot_words$name <- as.factor(tot_words$name)

tot_words <- tot_words %>%
  distinct(name, .keep_all = T) %>%
  select(-word)
  
tot_words <- merge(x = data[, c("name", "CO_year", "dummy_exitoso_OVE")], 
                   y = tot_words, by = "name")

tot_words %>%
  group_by(dummy_exitoso_OVE) %>%
  get_summary_stats(total_words, type = "mean_sd")

tot_words %>%
  group_by(CO_year) %>%
  get_summary_stats(total_words, type = "mean_sd")


tot_words %>%
 anova_test(total_words ~ dummy_exitoso_OVE) 

tot_words %>%
 anova_test(total_words ~ CO_year) 

tot_words %>%
 summarise(mean = mean(total_words), sd = sd(total_words))

tot_words %>%
  mutate(name = reorder(name, total_words)) %>%
  ggplot(aes(name, total_words, color = CO_year)) +
  geom_errorbar(aes(ymin = 0, ymax = total_words), linetype = "dashed", width=0) +
  geom_point(aes(size = .1)) +
  guides(size = FALSE, col = guide_legend("Closing Year")) +
  labs(x = "", y = "Total number of words") +
  coord_flip() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "bottom",
    legend.margin = margin(300,10,10,10),
    legend.text = element_text(size = 25)
    ) 
  

```

## 3. Creating corpus

```{r}
library(tidytext)
# Create corpus
corpus <- Corpus(VectorSource(as.vector(full_text$word))) 
new_corpus <- tm_map(corpus, content_transformer(tolower))
new_corpus <- tm_map(new_corpus, stripWhitespace)

# remove stoping words
stop_words <- stopwords::stopwords("es")
new_corpus <- tm_map(new_corpus, removeWords, stop_words) 

# stem corpus
stem_corpus <- tm_map(new_corpus, content_transformer(stemDocument), language = "spanish")

# we correct some of the stems to its right root
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), pattern = "policial", 
                      replacement = "polici")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "energi|energet", replacement = "energ")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "comercial", replacement = "comerci")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "inocu", replacement = "inocuidad")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "turism", replacement = "turist")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "catastral", replacement = "catastr")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "emprendedor", replacement = "emprend")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "porcentual", replacement = "porcent")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "institucional", replacement = "institu")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "nacional", replacement = "nacio")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "provincial", replacement = "provinci")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "pobrez", replacement = "pobr")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "transferent", replacement = "transferenc")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "presupuestari", replacement = "presupuest")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "municipal", replacement = "municip")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "municipi", replacement = "municip")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "promocion", replacement = "promo")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "elegible|elegibilidad|elegibles", replacement = "eleg")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "financier", replacement = "financ")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "tecnologi", replacement = "tecnolog")
stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = "percepcion", replacement = "percep")

stem_corpus <- tm_map(stem_corpus, content_transformer(gsub), 
               pattern = ".cion*", replacement = "")

 
# test <- c("comercializacion", "distribucion", "administracion", "comercializ", "emprendedurismo",
#         "distrib", "administr", "puert", "institucionaliza", "funcion", "dotacion")
# gsub(".cion*$", "", test)
# grep("\\b[[:alpha:]]{9,}\\b", test, value = T)
# gsub("(.cion$)|(\\b[[:alpha:]]{1,9}\\b)", "", test)
# 
# 
# for (i in 1:length(stem_corpus)) {
#    full_text$word[i] <- stem_corpus$content[[i]]
# }


```

## Convert to dtm and tidy text

```{r}
# Create Document-term matrix
dtm <- DocumentTermMatrix(stem_corpus, control = list(wordLengths = c(2, Inf)))
inspect(dtm)

# Remove sparse terms
#dtm <- removeSparseTerms(dtm, .975)

#Convert dfm to tidy text (to get the tokens)
td_data <- tidy(dtm)
td_data$document <- as.factor(td_data$document)

# We create a group id
full_text <- full_text %>%
  group_by(name) %>%
  arrange(name) %>%
  mutate(document = as.factor(cur_group_id()))
  
# We merge to get the PCR id
td_data <- left_join(td_data, full_text[, c("name", "document")],
                       by = "document", copy = FALSE)

td_data <- td_data[, 2:4] # we get rid of the index

```

# removing unneccesary stuff 

```{r}
rm(outlist)
rm(corpus)
rm(new_outlist)
rm(new_corpus)
rm(more_stopping)
rm(more_stopping2)

```

## 3.1 Merge text data with OVE data

```{r}
# remove one to three-character words and more stopping words
td_data <- td_data %>%
  filter(!term %in% mystopwords) %>% 
  mutate(term = gsub("\\b[[:alpha:]]{1,3}\\b","", term)) %>%
  filter(term!= "") %>%
  filter(term!= '"')

#grams$name <- as.character(grams$name)

new_data <- merge(x = data[, c("name", "OVERating", "dummy_exitoso_OVE", "dummy_exitoso_MGT",   
                                "OVERelevancerating", "CO_year", "Dep", "Div")], 
                  y = td_data, by = "name")

new_data$name <- as.factor(new_data$name)

new_data %>%
  distinct(term) %>%
  count()



```

# 4. Sectoral composition


```{r}
data.sector <- new_data %>%
  distinct(name, .keep_all = T)

white <- theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
               panel.background = element_blank(), axis.line = element_line(colour =
                                                                              "white"))
center <- theme(plot.title = element_text(hjust = 0.5))

legend_tit <- "CO year"

  
data.sector %>% 
  group_by(Dep, CO_year) %>% 
    count() %>%
    arrange(CO_year, desc(Dep)) %>%
    group_by(CO_year) %>% 
    mutate(n2 = cumsum(n), prop = round(100*n/sum(n))) %>% 
    ggplot(aes(fill = CO_year, x = Dep , y = prop)) +
    scale_fill_brewer(palette = "Set2") + 
    geom_bar(position = "dodge", stat = "identity") + 
        geom_text(aes(label = prop), position = position_dodge(width=0.9),vjust = 1.2) +
        scale_y_continuous(name = "") + white + xlab("") + center +
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "bottom",
    legend.margin = margin(-15,-7, -70,0),
    legend.title = element_blank(),
    legend.text = element_text(size = 15)
    ) 
  
data.sector %>% 
  group_by(Div, CO_year) %>% 
    count() %>%
    ggplot(aes(fill = CO_year, x = Div , y = n)) +
    scale_fill_brewer(palette = "Set2") + 
    geom_bar(position = "dodge", stat = "identity") + 
        geom_text(aes(label = n), position = position_dodge(width=0.9),vjust=1.2) +
        scale_y_continuous(name = "") + white + xlab("") + center +
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "bottom",
    legend.margin = margin(-15,-10, -70,0),
    legend.title = element_blank(),
    legend.text = element_text(size = 15)
    ) 
  

```


# 5. Exploratory Data Analysis

## 5.1 Analyzing most frequent terms with Word clouds


```{r}
if (!require("wordcloud2")) install.packages("wordcloud2"); library("wordcloud2")
# Frequency of words
td_data %>%
   group_by(term) %>%
   mutate(N = sum(count)) %>%
   distinct(term, .keep_all = T) %>%
   arrange(desc(freq)) %>%
   ungroup() %>%
   filter(N >= 500) %>%
   mutate(term = reorder(term, -N)) %>%
   ggplot(aes(term, N)) +
        geom_bar(stat = "identity", fill = "darkred", colour = "darkgreen") +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))  + white +
        xlab("") + ylab("Frequency") +
  scale_y_continuous(breaks=seq(0, 3800, by = 500)) 

# word clouds
set.seed(1001)
new_data %>%
   group_by(term) %>%
   mutate(count = sum(count)) %>%
   distinct(term, .keep_all = T) %>%
   arrange(desc(count)) %>%
   #filter(count < 1000) %>%
   ungroup() %>%
   #filter(dummy_exitoso_OVE == "Successful") %>%
   top_n(100, count) %>%
   filter(term!= "",
   !term %in% c("mism", "trav", "plaz", "tabl", "neral", "medi", "equip", "pued",
                "tambi", "atencion", "alcanz", "asoci", "mayor", "menor", 
                "respect", "gener", "numer", "accion", "nuev", "esper")) %>%
    with(wordcloud(term, count, max.words = 100, random.order=FALSE, rot.per = 0.35,
          scale=c(4.1,0.6), colors = brewer.pal(8, "Dark2")))

set.seed(1001)
w.cloud <- new_data %>%
   group_by(term) %>%
   mutate(count = sum(count)) %>%
   distinct(term, .keep_all = T) %>%
   arrange(desc(count)) %>%
   #filter(count < 1000) %>%
   ungroup() %>%
   top_n(119, count) %>%
   select(term, count)
   
colorVec = rep(c('skyblue', "gray", "lightgray", "black"), length.out = nrow(w.cloud))
wordcloud2(data = w.cloud, size = .8, shape= "oval", color = colorVec)


```


## 5.2 Analyze data with td-idf 

```{r}
library(gtable)
library(ggplot2)
library(tidyverse)
library(tm)
library(gridExtra)
library(grid)

bind_tf_idf <- new_data %>%
  bind_tf_idf(term = term, document = name, n = count)

bind_tf_idf <- bind_tf_idf %>%
  mutate(rank = row_number(tf_idf)) %>%
   arrange(desc(rank)) 

bind_tf_idf %>%
  ggplot(aes(rank, tf_idf, color = name)) +
  geom_line(size = 1.1, alpha = .8, show.legend = F) +
  labs(x = "Rank of terms ordered by TF-IDF",
       y = "TF-IDF value") +
  scale_x_continuous(breaks=seq(0,36700, by = 10000)) + white +
         theme(axis.line = element_line(colour = "black")) +
         theme(legend.title = element_blank())  
  
bind_tf_idf %>%
  filter(tf_idf != 0) %>% 
  filter(tf_idf <= .001) %>%
  count()

bind_tf_idf %>%
  group_by(dummy_exitoso_OVE) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(term = reorder(term, tf_idf)) %>%
  ggplot(aes(term, tf_idf, fill = dummy_exitoso_OVE)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~dummy_exitoso_OVE, scales = "free") +
  theme(panel.background = element_blank(),
        strip.text = element_text(size = 15),
        axis.title.x =element_blank(),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 11),
        axis.title.y = element_blank()) +
  labs(y = "Term frequency inverse document frequency") +
  coord_flip()

```


## 5.3 Word frequency distribution

```{r}

bind_tf_idf %>%
  distinct(term)%>%
  count()

bind_tf_idf %>%
  filter(term == "turist") %>%
  select(name, term, count)

bind_tf_idf %>%
  filter(term == "canton") %>%
  select(name, term, count)

bind_tf_idf %>%
  group_by(term) %>%
  mutate(N = sum(count)) %>%
  ungroup() %>%
  distinct(term, .keep_all = T) %>%
  select(term, count, N) %>%
  arrange(desc(N)) 

bind_tf_idf %>%
  group_by(term) %>%
  mutate(N = sum(count)) %>%
  ungroup() %>%
  distinct(term, .keep_all = T) %>%
  arrange(desc(N)) %>%
  filter(N > 100) %>%
  mutate(term = reorder(term, -N)) %>%
  ggplot(aes(term, N)) +
        geom_bar(stat = "identity", fill = "darkred", colour = "darkgreen") +
        theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + white +
        #theme(axis.text.x = element_text(angle = 90, hjust = 1))  + white +
        xlab("Term in Corpus") + ylab("Frequency") +
  scale_y_continuous(breaks=seq(0, 3800, by = 500)) 
  #geom_hline(yintercept = 380, linetype = "dotted", color = "blue")


```


## 5.4 Vocabulary adjustment

## 5.4.1 Remove words with tf-idf equal to zero

```{r}
bind_tf_idf %>%
  group_by(term) %>%
  mutate(N = sum(count)) %>%
  ungroup() %>%
  filter(tf_idf == 0) %>%
  distinct(term, .keep_all = T) %>%
  arrange(desc(N)) %>%
  select(term, N, tf_idf) %>% View()

low.tfidf <- bind_tf_idf %>%
  group_by(term) %>%
  mutate(N = sum(count)) %>%
  ungroup() %>%
  filter(tf_idf == 0) %>%
  distinct(term, .keep_all = T) %>%
  arrange(desc(N)) %>%
  select(term) %>% 
  pull()

tf_new <- bind_tf_idf %>%
 filter(!term %in% low.tfidf) %>%
 arrange(desc(tf_idf))

tf_new %>%
    group_by(term) %>%
    mutate(N = sum(count)) %>%
    ungroup() %>%
    mutate(term = reorder(term, -N)) %>%
    distinct(term, .keep_all = T) %>%
    arrange(desc(N)) %>% select(term, N, tf, tf_idf) %>% View()

tf_new %>%
  distinct(term) %>%
  count()

tf_new %>%
  group_by(term) %>%
  mutate(N = sum(count)) %>%
  ungroup() %>%
  mutate(term = reorder(term, -N)) %>%
  distinct(term, .keep_all = T) %>%
  arrange(desc(N)) %>%
  filter(N > 50) %>%
  mutate(term = reorder(term, -N)) %>%
  ggplot(aes(term, N)) +
        geom_bar(stat = "identity", fill = "darkred", colour = "darkgreen") +
        theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + white +
        #theme(axis.text.x = element_text(angle = 90, hjust = 1))  + white +
        xlab("Term in Corpus") + ylab("Frequency") + 
  scale_y_continuous(breaks=seq(0, 900, by = 100)) 
  #geom_hline(yintercept = 380, linetype = "dotted", color = "blue")

tf_new %>%
  group_by(term) %>%
  mutate(N = sum(count)) %>%
  ungroup() %>%
  mutate(term = reorder(term, -N)) %>%
  distinct(term, .keep_all = T) %>%
  arrange(desc(N)) %>%
  filter(N > 200) %>%
  mutate(term = reorder(term, -N)) %>%
  ggplot(aes(term, N)) +
        geom_bar(stat = "identity", fill = "darkred", colour = "darkgreen") +
        theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + white +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))  + white +
        xlab("Term in Corpus") + ylab("Frequency") + 
  scale_y_continuous(breaks=seq(0, 900, by = 100)) 
  #geom_hline(yintercept = 380, linetype = "dotted", color = "blue")


# tf_rank %>%
#   group_by(dummy_exitoso_OVE) %>%
#   top_n(10) %>%
#   ungroup() %>%
#   mutate(term = reorder(term, tf_idf)) %>%
#   ggplot(aes(term, tf_idf, fill = dummy_exitoso_OVE)) +
#   geom_col(show.legend = FALSE) +
#   facet_wrap(~dummy_exitoso_OVE, scales = "free") +
#   theme(panel.background = element_blank(),
#         axis.title.x=element_blank(),
#         axis.title.y=element_blank()) +
#   labs(y = "Term frequency inverse document frequency") +
#   coord_flip()

```

## 5.4.2 Histogram for repetition of terms across documents

```{r}
doc.rep <- tf_new %>%
  add_count(term, name = "document_total") %>%
  group_by(term) %>%
  mutate(N = sum(count)) %>%
  distinct(term, .keep_all = T) %>%
  select(term, document_total, N) %>%
  arrange(desc(document_total, N)) %>%
  group_by(document_total) %>%
  summarize(n = n())

doc.rep %>%
  filter(document_total > 1) %>%
  #mutate(rep = reorder(document_total, -n)) %>%
  ggplot(aes(document_total, n)) +
        geom_bar(stat = "identity", fill = "darkred", colour = "darkgreen") +
        theme(axis.text.x = element_text(angle = 0, hjust = .5, 
                          vjust = 1.5, margin = unit(c(0,0,3,0), "mm")))  + white +
        xlab("Number of documents in the corpus") + ylab("Number of unique terms") + 
        scale_x_continuous(breaks=seq(1, 42, by = 1)) +
        scale_y_continuous(breaks=seq(0, 1000, by = 100), expand = c(0,0))



```

## 5.4.3 Remove words from both tails

```{r}
# tf_new %>%
#   add_count(term, name = "document_total") %>%
#   filter(document_total >= 37) %>%
#   distinct(term) %>% View()

right.tail <- tf_new %>%
  add_count(term, name = "document_total") %>%
  filter(document_total >= 37) %>%
  distinct(term) %>%
  select(term) %>%
  pull(term)

left.tail <- tf_new %>%
  add_count(term, name = "document_total") %>%
  filter(document_total <= 4) %>%
  distinct(term) %>%
  select(term) %>%
  pull(term)

single.words <- tf_new  %>%
  filter(count > 120) %>%
  select(term) %>%
  pull(term)

tf_clean <- tf_new %>%
  filter(!term %in% right.tail) %>%
  filter(!term %in% left.tail) %>%
  filter(!term %in% single.words) %>%
  filter(!term %in% c("desembols", "parcial", "eleg", "limit", "obras", "prest", "destin",
                      "manten")) %>%
  arrange(desc(tf_idf))

tf_clean %>% 
  distinct(term) %>%
  count()

# We plot tf-idf words by type of project (OVE)
tf_clean %>%
  select(term, tf_idf, dummy_exitoso_OVE)%>%
  filter(!term %in% c("atra", "vall")) %>%
  group_by(dummy_exitoso_OVE,term)%>%
  filter(tf_idf == max(tf_idf))%>%
  group_by(dummy_exitoso_OVE)%>%
  top_n(10,tf_idf)%>%
  ungroup()%>%
  mutate(term = reorder_within(term,tf_idf, dummy_exitoso_OVE))%>%
  ggplot(aes(tf_idf,term,fill=dummy_exitoso_OVE))+
  geom_col(show.legend = FALSE)+
  theme(panel.background = element_blank(),
        strip.text = element_text(size = 15),
        axis.title.x =element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.y=element_blank()) +
  scale_y_reordered()+
  facet_wrap(~dummy_exitoso_OVE, scales='free_y')

tf_clean %>%
  filter(term == "moderniz") %>%
  select(name, term, count)



```



## Pairwise correlations


```{r}
# library(widyr)
# library(ggraph)
# library(tidygraph)
# 
# corr_single <- new_data %>%
#   #filter(dummy_exitoso_OVE == "Successful") %>%
#   filter(n >= 4) %>%
#   select(-n) %>%
#   #select(-name) %>%
#   select(-OVERating) %>%
#   select(-dummy_exitoso_OVE) %>%
#   select(-OVERelevancerating) %>%
#   pairwise_cor(word, name, sort = TRUE)
# 
# corr_single %>%
#   filter(item1 %in% c("evaluación")) %>%
#       group_by(item1) %>%
#       top_n(5) %>%
#       ungroup() %>%
#       mutate(item2 = reorder(item2, correlation)) %>%
#       ggplot(aes(item2, correlation)) +
#       geom_col(fill = "lightskyblue") +
#       xlab("Correlation coefficient") + ylab("") +
#       facet_wrap(~ item1, scales = 'free') +
#       coord_flip()

  
```


## 6. Topic modeling: Latent Dirichlet Allocation  

## 6.1 Find optimal number of topics

```{r}
install.packages("ldatuning")
install.packages("furrr")
library("topicmodels")
library("ldatuning")
library("stm")
library("quanteda")
library("furrr")

review_matrix <- tf_clean %>%
  cast_sparse(name, term, count)

# to find the optimar number of topics
result <- FindTopicsNumber(
  review_matrix,
  topics = seq(from = 2, to = 30, by = 1),
  metrics = c("CaoJuan2009", "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 77),
  mc.cores = 3L,
  verbose = TRUE
)

FindTopicsNumber_plot(result)

#Extremely time-consuming
set.seed(123)
train.vector <- sample(48,21,replace = F)
train.vector

text_train.dtm <- dtm[!(dtm$dimnames$Docs %in% train.vector),]
text_test.dtm <- dtm[dtm$dimnames$Docs %in% train.vector,]
# 
# #table(text_train.dtm$i)
# #table(text_test.dtm$i)
# tuning <- FindTopicsNumber(
#   dtm = text_train.dtm,
#   topics = seq(from = 2, to = 30, by = 1),
#   metrics = c("CaoJuan2009", "Deveaud2014"),
#   method = "Gibbs",
#   control = list(seed = 77),
#   mc.cores = 2L,
#   verbose = TRUE
# )
# 
# FindTopicsNumber_plot(tuning)

# Using perplexity to determine number of topics

n_topics <- c(2, 4, 10, 20, 50, 100)

lda_compare <- n_topics %>%
    furrr::future_map(LDA, x = review_matrix, control = list(seed = 1234))

tibble(k = n_topics,
       perplex = map_dbl(lda_compare, perplexity)) %>%
  ggplot(aes(k, perplex)) +
  geom_point() +
  geom_line() + 
  labs(x = "Number of topics",
       y = "Perplexity") +
  scale_x_continuous(breaks=seq(0,100, by = 2)) + white +
         theme(axis.line = element_line(colour = "black")) +
         theme(legend.title = element_blank()) 

#Using training and testing data
perplexity_df <- data.frame(train=numeric(), test=numeric())
topics <- c(2:30)
burnin = 100
iter = 100
keep = 50

set.seed(12345)
for (i in topics){

  fitted <- LDA(text_train.dtm, k = i, method = "Gibbs",
                control = list(burnin = burnin, iter = iter, keep = keep) )
  perplexity_df[i,1] <- perplexity(fitted, newdata = text_train.dtm)
  perplexity_df[i,2]  <- perplexity(fitted, newdata = text_test.dtm)
}

##plotting the perplexity of both train and test

gg.names <- c("Training" , "Testing")
colnames(perplexity_df) <- gg.names

ggplot(perplexity_df, aes(as.numeric(row.names(perplexity_df)))) +
      labs(y = "Perplexity", x = "Number of topics") +
      scale_y_continuous(breaks = seq(0,1900, by = 100)) +
      scale_x_continuous(breaks = seq(0, 30, 1)) + theme_minimal() +
         geom_line(aes(y = Testing, colour = "Training")) +
         geom_line(aes(y = Training, colour = "Testing")) + white +
         theme(axis.line = element_line(colour = "black")) +
         theme(legend.title = element_blank()) +
    theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "bottom",
    legend.margin = margin(0,0, -40,0),
    legend.text = element_text(size = 15)
    )
     
  


```

## 6.2 Estimating topics

```{r}
## WE ESTIMATE OUR LDA MODEL WITH 14 TOPICS

lda <- LDA(review_matrix, k = 12, control = list(seed = 1235))

td_beta <- tidy(lda, matrix = "beta")

td_beta %>%
  group_by(topic) %>%
  top_n(7, beta) %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  scale_y_reordered() +
  facet_wrap(~ topic, scales = "free_y") +
  theme(axis.title.y=element_blank()) +
  labs(title = "Words with highest probability in each of the 12 topics")

# Heat map
data.hmap <- td_beta %>%
  group_by(topic) %>%
  top_n(7, beta)%>%
  ungroup()%>%
  arrange(topic,  desc(beta)) %>%
  group_by(topic) %>%
  mutate(n = 1:n_distinct(term)) %>%
  group_by(topic) %>%
  mutate(perc = n/sum(n))%>%
  mutate(topic = paste0("topic", topic))

data.hmap$topic <- factor(data.hmap$topic, levels =
                        c("topic1","topic2","topic3","topic4","topic5","topic6","topic7",
                          "topic8","topic9","topic10", "topic11", "topic12"))

data.hmap$topic <- fct_rev(data.hmap$topic) # reverse order of topics

max(data.hmap$beta)

data.hmap %>%
  group_by(topic) %>%
  ggplot(aes(n, topic, fill = beta)) +
  geom_tile()+
  geom_text(aes(label = term), size = 3)+
  scale_fill_gradient(low = "white",high = "purple",
                      breaks = c(0, .025, .04668716), labels = c("0", ".025", ".050"),
                      limits = c(0, .047)) + 
   theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_text(margin=margin(10,-7,0,10,"mm")),
        axis.ticks.x = element_blank()) + white +
  theme(legend.key.height = unit(5.45, "line")) +
  theme(legend.title = element_blank()) 


```

## 6.4 Topic assignment 

```{r}
td_gamma <- tidy(lda, matrix = "gamma")
ggplot(td_gamma, aes(gamma, fill = as.factor(topic))) +
  geom_histogram(show.legend = F) +
  facet_wrap(~topic, ncol = 3)

# dist_topic <- dcast(td_gamma, document~topic, value.var = "gamma")
# 
# sum(dist_topic$"1")/nrow(dist_topic)
# sum(dist_topic$"2")/nrow(dist_topic)
# sum(dist_topic$"3")/nrow(dist_topic)
# sum(dist_topic$"4")/nrow(dist_topic)
# sum(dist_topic$"5")/nrow(dist_topic)
# sum(dist_topic$"6")/nrow(dist_topic)
# sum(dist_topic$"7")/nrow(dist_topic)
# sum(dist_topic$"8")/nrow(dist_topic)
# sum(dist_topic$"9")/nrow(dist_topic)
# sum(dist_topic$"10")/nrow(dist_topic)
# sum(dist_topic$"11")/nrow(dist_topic)
# sum(dist_topic$"12")/nrow(dist_topic)

td_gamma$document <- as.factor(td_gamma$document)
td_gamma$topic <- as.factor(td_gamma$topic)

td_gamma$gamma <- round(td_gamma$gamma, 6) #rounding

topic_docs <- td_gamma %>%
  group_by(document) %>%
  top_n(1, gamma) 

# Topic assignment per document
max_gamma <- td_gamma %>%
  group_by(document) %>%
  top_n(1, gamma) %>%
  ungroup() %>%
  group_by(topic) %>%
  summarize(n = n()) %>%
  mutate(n2 = cumsum(n), prop = round(100*n/sum(n), 1)) %>%
  arrange(desc(topic)) %>%
  mutate(ymax = cumsum(prop))
  
max_gamma$ymin = c(0, head(max_gamma$ymax, n=-1))  
max_gamma$labelPosition <- (max_gamma$ymax + max_gamma$ymin) / 2

max_gamma$topic <- factor(max_gamma$topic,
    levels = c(1:12),
    labels = c("Labor and Unemployment", "Citizen Security / Natural Disaster Management",
               "Improve Learning in Education / SME", "Neonatal and Maternal Mortality",
               "Agricultural and Livestock Innovation", "Entrepreneurship and Commerce",
               "Land Tenure Regularization", "Increasing Electricity Coverage",
               "Road Safety", "Community Services", "Water and Sanitation Services",
               "Rehabilitation-Modernization of Public Services"))

nb.cols <- 12
mycolors <- colorRampPalette(brewer.pal(7, "Set3"))(nb.cols)
legend_title <- ""

max_gamma %>%
  ggplot(aes(ymax = ymax, ymin = ymin, xmax = 9, xmin = 8, fill = topic)) +
     geom_rect() +
     geom_text(x = 8.5, aes(y = labelPosition, label = n), 
                colour =  "black", size = 4.4, 
                show.legend = FALSE) +
     scale_fill_manual(legend_title, values = mycolors) +
     coord_polar(theta = "y") +
     xlim(c(2, 9)) +
     theme_void() +
     theme(axis.text.x=element_blank()) + theme(legend.position=c(.51, .52)) +
     theme(panel.grid=element_blank(),
           axis.text=element_blank(),
           axis.ticks=element_blank(),
           legend.title = element_text(),
           legend.text = element_text(size = 7.5)) 


```

## Check assignment

```{r}
levels(topic_docs$topic) <- c("Labor and Unemployment", 
                              "Citizen Security / Natural Disaster Management",
               "Improve Learning in Education / SME", "Neonatal and Maternal Mortality",
               "Agricultural and Livestock Innovation", "Entrepreneurship and Commerce",
               "Land Tenure Regularization", "Increasing Electricity Coverage",
               "Road Safety", "Community Services", "Water and Sanitation Services",
               "Rehabilitation-Modernization of Public Services")

topic_docs$good_assign <- as.factor(ifelse(topic_docs$gamma >= .9, 1, 0))

topic_docs %>%
  group_by(good_assign) %>%
  count()


```


## 6.5 External rating from OVE and topics

```{r}
labels.OVE <- tf_clean %>%
  distinct(name, dummy_exitoso_OVE) %>%
  mutate(document = name) %>%
  select(document, dummy_exitoso_OVE)

topic_docs <- left_join(topic_docs, labels.OVE,
                       by = "document", copy = FALSE)

test <- topic_docs %>%
  group_by(topic) %>%
  mutate(n_topics = n()) %>%
  ungroup() %>%
  group_by(topic, dummy_exitoso_OVE) %>%
  mutate(n = n()) %>%
  arrange(topic, desc(dummy_exitoso_OVE)) %>%
  mutate(prop = round((n/n_topics)*100)) %>%
  distinct(topic, dummy_exitoso_OVE, prop)

test  %>%
  ggplot(aes(fill = dummy_exitoso_OVE, x = topic, y = prop)) +
    geom_bar(position = "stack", stat = "identity", width=0.9) +
    geom_text(aes(label = paste0(prop,"%")), position = position_stack(vjust = 0.5), size = 4) + 
    white + center + xlab("") + ylab("Percentage") +
    theme(
      axis.text.x = element_text(angle = 90, size = 8),
      legend.title = element_blank())

  

  

```




## 6.6 Topic Similarity 

```{r}
library(reshape2)

topic.term <- dcast(td_beta, topic ~ term)
topic.term <- topic.term[, -1]
topic.term <- topic.term %>%
  mutate_all(round, 4)


# max <- colnames(topic.term)[apply(topic.term, 1, which.max)]
# vmax <- topic.term[apply(topic.term, 1, which.max)]
# maxn <- function(n) function(x) order(x, decreasing = TRUE)[n]
# test <- apply(topic.term, 1, function(x)x[maxn(2)(x)])

lda.similarity <- topic.term %>%
  scale() %>%
  dist(method = "euclidean") %>%
  hclust(method = "ward.D2")

par(mar = c(0, 4, 4, 2))
dev.off()
plot(lda.similarity,
     main = "LDA topic similarity by features",
     xlab = "",
     sub = "")

```




